Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-01-31 paper/zhang-cook-laa-langrene-menendez.Rmd
polish section done

```{r polish, fig.height= 2.5, fig.cap = "Two-D projection on \\code{boa6} data with holes index optimised by pseudo derivative. The left panel shows the final projected data before polish and the right panel shows the one after. The separation of the clusters on the y axis becomes sharper after the polish. "}
```

Once the final basis has been found by an optimiser, one may want to push further in the close neighbourhood to find an even better basis. A polish search takes the final basis as the start of a new guided tour to search for local breakthrough.

The polish algorithm is similar to the simulated annealing one with three main distinctions on 1) the number of candidate basis generated each time in the inner loop; 2) the search neighbourhood, `alpha`, and 3) the termination conditions. In simulated annealing, only one candidate basis $\mathbf{A}_l$ is generated every time while the polish algorithm allows for a specified number of basis to be evaluated for each repetition in the inner loop via an argument `n_sample`. The search neighbourhood in simulated annealing is reduced in the outer loop, that is, the alpha for one iteration of search remains the same, while in polish search, `alpha` is reduced once a set of candidate bases fails to make an improvement. To avoid the case the neighbourhood size becoming too small to generate meaningful search, more termination criteria have been added, apart from the original `max.tries` condition and  these include:

@@

Figure \ref{fig:polish} presents the final projections found before (left) and after(right) applying the polish using the pseudo derivative optimiser. Before polishing, the four clusters are clearly shown while the edges of each cluster is relatively unshaved. The polish search start with this basis and on the right panel, the edges of the clusters are better trimmed.

>>>>

```{r polish, fig.height= 5, fig.cap = "Trace plot of 2D projection on \\code{boa6} data with holes index, optimised first by SA and then by polish search. The polish step results in clearer cut on the edges of the four clusters in the data structure."}
```

Once the final basis has been found by an optimiser, one may want to push further in the close neighbourhood to see if an even better basis can be found. A polish search takes the final basis of an optimiser as the start of a new guided tour to search for local breakthrough. The polish algorithm is similar to the SA with three main distinctions: 1) 100 rather than one candidate bases are generated each time in the inner loop; 2) the search neighbourhood, `alpha`, is reduced in the inner loop, rather than in the outer loop, once a set of candidate bases fails to make an improvement; and 3) three more termination conditions have been added to ensure the new basis generated is distinguishable from the current in terms of the distance in the space,  percentage change in the index value, and neighbourhood:

@@

Figure \ref{fig:polish} presents the trace plot of a 2D projection, optimised by SA and followed by the polish search, along with the projection on the final basis of each algorithm. The end basis found by SA reveals the four clusters in the data, but the edges of each cluster are not clean-cut. Polish works with this end basis and further pushes the index value to produce even clear structure in the data. One can observe that the projection after polishing better distinguishes the four clusters with more trimmed edges, espeically along the vertical axis.

### 2021-01-31 paper/zhang-cook-laa-langrene-menendez.tex
polish section done

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/polish-1} \caption[Two-D projection on \code{boa6} data with holes index optimised by pseudo derivative]{Two-D projection on \code{boa6} data with holes index optimised by pseudo derivative. The left panel shows the final projected data before polish and the right panel shows the one after. The separation of the clusters on the y axis becomes sharper after the polish. }\label{fig:polish}
\end{figure}
\end{Schunk}

Once the final basis has been found by an optimiser, one may want to
push further in the close neighbourhood to find an even better basis. A
polish search takes the final basis as the start of a new guided tour to
search for local breakthrough.

The polish algorithm is similar to the simulated annealing one with
three main distinctions on 1) the number of candidate basis generated
each time in the inner loop; 2) the search neighbourhood,
\texttt{alpha}, and 3) the termination conditions. In simulated
annealing, only one candidate basis \(\mathbf{A}_l\) is generated every
time while the polish algorithm allows for a specified number of basis
to be evaluated for each repetition in the inner loop via an argument
\texttt{n\_sample}. The search neighbourhood in simulated annealing is
reduced in the outer loop, that is, the alpha for one iteration of
search remains the same, while in polish search, \texttt{alpha} is
reduced once a set of candidate bases fails to make an improvement. To
avoid the case the neighbourhood size becoming too small to generate
meaningful search, more termination criteria have been added, apart from
the original \texttt{max.tries} condition and these include:

>>>>

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/polish-1} \caption[Trace plot of 2D projection on \code{boa6} data with holes index, optimised first by SA and then by polish search]{Trace plot of 2D projection on \code{boa6} data with holes index, optimised first by SA and then by polish search. The polish step results in clearer cut on the edges of the four clusters in the data structure.}\label{fig:polish}
\end{figure}
\end{Schunk}

Once the final basis has been found by an optimiser, one may want to
push further in the close neighbourhood to see if an even better basis
can be found. A polish search takes the final basis of an optimiser as
the start of a new guided tour to search for local breakthrough. The
polish algorithm is similar to the SA with three main distinctions: 1)
100 rather than one candidate bases are generated each time in the inner
loop; 2) the search neighbourhood, \texttt{alpha}, is reduced in the
inner loop, rather than in the outer loop, once a set of candidate bases
fails to make an improvement; and 3) three more termination conditions
have been added to ensure the new basis generated is distinguishable
from the current in terms of the distance in the space, percentage
change in the index value, and neighbourhood:
